Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex

The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Columns with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

@@

To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to about 100, while other tools got almost the same number of timouts with the results of timeout set to 10s. Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits). These problems ask for a model of a valid credit card number as a string of length 2 to 12 each case. We ran these tests additionally to the experiments above with the timeout set to 120s. In these tests, {\tool} can solve all 11 problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve these problems (either timeout or UNKNOWN). However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops. It seems that Z3 has some strategies that can solve problems of even loops efficiently. \todo{Update table with data of timeout=30s}

>>>>

The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae. Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
							& UNSAT    &    288  &   221 &   100 &   111 \\
							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
							& UNSAT    &    319  &   240 &   186 &   192 \\
							& $\times$ &    248  &   154 &   615 &   382 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
							& UNSAT    &    820  &   818 &   808 &   772 \\
							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 \\
							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

@@

To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to 539, while CVC4 and Z3-str3 got almost the same number of timeouts with the results of timeout set to 10s. Z3 also managed to reduce the number of timeouts to 821. If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.

Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits). These problems ask for a model of a valid credit card number as a string of length 2 to 12  each case. We ran these tests additionally to the experiments above with the timeout set to 120s. In these tests, {\tool} can solve all 11 problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve these problems (either timeout or UNKNOWN). However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops. It seems that Z3 has some strategies that can solve problems of even loops efficiently.

% \todo{Update table with data of timeout=30s}
